Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-06 reanalysis-9-alternative_specifications.qmd
wip

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm",  # Completed successfully
  "nearest_gam",  # Completed successfully
  "nearest_gbm",  # Completed successfully
  "nearest_lasso",  # Completed successfully
  "nearest_rpart",  # Completed successfully
  "nearest_mahalanobis",  # Completed successfully
  "subclass_glm",  # Completed successfully
  "cbps",  # Completed successfully
  "entropy",  # Completed successfully
  "bart"  # Completed successfully
  # "twang_gbm"  # Failed - needs rerun after fix
)

>>>>

# Define completed methods (add to this list as methods complete successfully)
# Note: twang_gbm should load from reanalysis-4 cache, not run fresh
completed_methods <- c(
  "nearest_glm",  # Completed successfully
  "nearest_gam",  # Completed successfully
  "nearest_gbm",  # Completed successfully
  "nearest_lasso",  # Completed successfully
  "nearest_rpart",  # Completed successfully
  "nearest_mahalanobis",  # Completed successfully
  "subclass_glm",  # Completed successfully
  "cbps",  # Completed successfully
  "entropy",  # Completed successfully
  "bart",  # Completed successfully
  "twang_gbm"  # Will load from reanalysis-4 cache
)
